% Preamble
\documentclass[11pt]{article}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Gal}{\text{Gal}}
\newcommand{\script}[1]{\mathscr{#1}}
\newcommand{\partialby}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\partialbytwo}[2]{\frac{\partial^2{#1}}{\partial{#2}^2}}
\newcommand{\partialbyoneone}[3]{\frac{\partial^2{#1}}{\partial{#2} \partial{#3}}}
\newcommand{\mtx}[4] {\left[\begin{matrix} #1 & #2 \\ #3 & #4  \end{matrix}\right]}
\newcommand{\cmtx}[2]{\left[\begin{array}{c} #1 \\ #2 \end{array} \right]}
\newcommand{\rmtx}[2]{\left[\begin{array}{cc} #1 & #2 \end{array} \right]}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\norm}[1]{\|#1\|}
\newcommand{\lang}{\langle}
\newcommand{\rang}{\rangle}
\newcommand{\abrack}[1]{\lang #1 \rang}
\newcommand{\bra}[1]{\langle #1 |}
\newcommand{\ket}[1]{| #1 \rangle}
\newcommand{\braket}[2]{\langle #1 | #2 \rangle}
\newcommand{\floor}[1]{\lfloor #1 \rfloor}
\usepackage{amsmath, amsthm, amsfonts, amstext, amscd, amssymb, amsthm, fullpage, mathrsfs, color, verse, nopageno, tipa}
\usepackage[top=.5in, bottom=.5in, left=1in, right=1in]{geometry}
\usepackage{titlesec}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\DeclareMathOperator{\tr}{Tr}
\newcommand*{\threeemdash}{\rule[0.5ex]{3em}{0.55pt}}
\newcommand*{\xdash}[1][3em]{\rule[0.5ex]{#1}{0.55pt}}
\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
% Theorem Styles
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
% Definition Styles
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\usepackage[parfill]{parskip}
\newtheorem*{prop}{Proposition}

\begin{document}

% Heading
	\title{The Last Temple of Lathander the Good}
	\date{\vspace{-24pt}}
	\author{Gabe Foster}
	\maketitle

\section{The Last Temple of Lathander the Good}

\begin{description}

\item[Hooks:] 

\begin{itemize}

\item{Screams echo from the temple of Lathander and a crowd scatters-- a zombie shambles out from the doors of the temple.}

\end{itemize}

\item[NPCs:]
\begin{description}

\item[Awakened Cor] This priest of Lathander is one of the few priests of the Morninglord that still wields some divine power.  It turns out, however, that that power is drawn from a darker place, as she was in fact the one who raised the zombie. She is part of a group that has corrupted Kelemvor's temple for the purpose of waking the undead, as an effort to rise up against noble rule. 

\item[Awakened Ria]

A recent addition to the ranks of Lathander's flock, Ria has come to command a great deal of respect from her colleagues.

\item[Attendants of the Temple]
Hilde (brusque, long blond hair), Ral (gregarious smile), and Ciara (shy, pixie cut).  

\end{description}

\item{Locations:}

\begin{itemize}

\item{The Last Temple of Lathander}

\item{Abandoned Temple of Kelemvor (and Dungeon Beneath}

\end{itemize}

\item{Player Interactions: }

Sage, Snart, and Althaea were contracted by Gili, a pockmarked thief based out of the Stones' Bones, to investigate the happenings around the Gods' Rest district. They encountered a zombie bursting forth from the halls of the Temple of Lathander, the Morninglord. Upon investigation, they discovered a trap door beneath Awakened Cor's study. Inside, they found a symbol of Lathander, covered in blood, and were attacked by a spectre. They defeated it, with Snart and Althaea grievously injured, due to some quick thinking from Sage. 

\end{description}

\end{document}