% Preamble
\documentclass[11pt]{article}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Gal}{\text{Gal}}
\newcommand{\script}[1]{\mathscr{#1}}
\newcommand{\partialby}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\partialbytwo}[2]{\frac{\partial^2{#1}}{\partial{#2}^2}}
\newcommand{\partialbyoneone}[3]{\frac{\partial^2{#1}}{\partial{#2} \partial{#3}}}
\newcommand{\mtx}[4] {\left[\begin{matrix} #1 & #2 \\ #3 & #4  \end{matrix}\right]}
\newcommand{\cmtx}[2]{\left[\begin{array}{c} #1 \\ #2 \end{array} \right]}
\newcommand{\rmtx}[2]{\left[\begin{array}{cc} #1 & #2 \end{array} \right]}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\norm}[1]{\|#1\|}
\newcommand{\lang}{\langle}
\newcommand{\rang}{\rangle}
\newcommand{\abrack}[1]{\lang #1 \rang}
\newcommand{\bra}[1]{\langle #1 |}
\newcommand{\ket}[1]{| #1 \rangle}
\newcommand{\braket}[2]{\langle #1 | #2 \rangle}
\newcommand{\floor}[1]{\lfloor #1 \rfloor}
\usepackage{amsmath, amsthm, amsfonts, amstext, amscd, amssymb, amsthm, fullpage, mathrsfs, color, verse, nopageno, tipa}
\usepackage[top=.5in, bottom=.5in, left=1in, right=1in]{geometry}
\usepackage{titlesec}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\DeclareMathOperator{\tr}{Tr}
\newcommand*{\threeemdash}{\rule[0.5ex]{3em}{0.55pt}}
\newcommand*{\xdash}[1][3em]{\rule[0.5ex]{#1}{0.55pt}}
\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
% Theorem Styles
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
% Definition Styles
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\usepackage[parfill]{parskip}
\newtheorem*{prop}{Proposition}

\begin{document}

% Heading
	\title{Grub and Music}
	\date{\vspace{-24pt}}
	\author{Gabe Foster}
	\maketitle

\section{Grub and Music}

\begin{description}

\item[Hooks:] 

\begin{itemize}

\item{Grub absent-mindedly rubs the key around his neck / someone asks Grub why he's sad.}

\item{Well informed denizens of the Westforest may have heard of the tower, and clerics of Sturm's hold may have heard of}

\end{itemize}

\item[NPCs:]
\begin{description}

\item[Grub (Athor Scrollkeeper):] Grub serves as the bouncer for the Rat's Ass Tavern. His grew up in the fortress of Sturm's Hold, where he fathered a daughter. His adherence to the traditional doctrines of a cleric of Dumathoin lead to the elopement of his daughter with a visiting wizard. 

He sought this wizard, and was not long in finding him-- alone, dead, and without his daughter. Around his neck was a finely wrought key, which Grub took. Upon trying the key in the lock of the wizard's abode, he heard the sound of a music box which was his daughters. Bashing his way inside, he found no sign of the girl. Trying it upon successive doors led to the same behavior. Eventually, Grub came to discover that the key played this music when turned. 

Decades of searching for his lost girl were fruitless, and now, centuries later, he finds himself alone and aging, a shadow of his former self.

\item[Alira Scrollkeeper:]
The daughter of Grub, long trapped in an enduring instance of Mordenkainen's Magical Mansion bound to the key to the music box by the wizard Cail upon his death. The years cooped up in the mansion have left her perilously close to losing the last thread of her sanity.

\item[Cail, High Wizard]

An expatriot Axian High Wizard, Cail established a tower on the fringe of the Pale Plains, Northeast of the Westforest and East of Sturm's Hold.  He traveled across the Icewater Headlands investigating symptoms (which motivated his flight from Axia) of increased undead activity across the region. His interest in this subject lead to his assasination by parties unknown upon his and Alira's elopement from Sturm's Hold.

\item[The Night's Face]

The Night's Face is a well-known guild of assassins. The have guildhouses in most large cities, and their modus operandi is simple: a life for a life.

\end{description}

\item{Locations:}

\begin{itemize}

\item{ The Rat's Ass Tavern }

\item{ Cail's Tower }

\item{ Sturm's Hold }

\end{itemize}

\end{description}

\end{document}